Adapting toolmark based chumbley score to bullets

### 2017-09-25 doc/aboutme.Rmd
checking some things

---
title: "Adapting toolmark based chumbley score to bullets"
author: "Ganesh, Heike"
date: "September 25, 2017"
output: html_document
---

@@

```{r echo=FALSE}

>>>>

---
title: "Adapting toolmark based chumbley score to bullets"
author: "Ganesh Krishnan, Heike Hofmann"
date: "September 25, 2017"
output: html_document
---

@@

![](../doc/plots/error_pt05.png)
For a significance level of 0.01

![](../doc/plots/error_pt01.png)

For a significance level of 0.001

![](../doc/plots/error_pt001.png)
